r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-10-28 r-package/paper2020/paper2020.Rmd
tweaks paper's introduction second paragraph

While there is a growing number of open source routing models [@opentripplanneropentripplanner; 
@lovelace2019stplanr; @padgham2019dodgr], most options available do not efficiently 
process large transport networks. More importantly, these softwares generate
deterministic estimates of travel times without accounting for issues of service
reliability (REF) and they only return the fastest route option between a set of
origins and destinations. This simple approach overlooks how often people's 
actual route choices deviate from shortest travel time paths, what
can occur due to multiple factors such as imperfect information, monetary costs 
and safety issues [@larsen2011travel; @zhu2015people; @conway2019getting].

>>>>

While there is a growing number of open source routing models [@opentripplanneropentripplanner; 
@lovelace2019stplanr; @padgham2019dodgr], most options available do not efficiently 
process large transport networks. More importantly, these softwares generate
deterministic estimates of travel times without accounting for variability in 
results (due to service reliability issues, for example) and only return the 
fastest route option between a set of origins and destinations (see @conway2018accounting 
for a more in-depth discussion). This simple approach overlooks how often people's 
actual route choices deviate from shortest travel time paths, what
can occur due to multiple factors such as imperfect information, monetary costs 
and safety issues [@larsen2011travel; @zhu2015people; @conway2019getting].
